---
title: "assignment4"
author: "yiwang"
date: "2023-11-24"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Option A -- Strings and functional programming in R

## exercise 1 

I will use the tidytext package to remove the common stopwords

first install the required package

```{r}
#install.packages("janeaustenr")
#install.packages("tidytext")

```

then load the required packages

```{r}
library(janeaustenr)
library(tidytext)
library(dplyr)
library(ggplot2)
library(stringr)
```

first load the book , i will use "pride and prejudice" as example

```{r}
text <- austen_books() %>%
  filter(book == "Pride & Prejudice")

head(text)
```

then break the text into individual words

```{r}
words <- text %>%
   unnest_tokens(word, text)
words
```

then remove the stop words using stop_words

```{r}
data("stop_words")
filtered_words <- words %>%
  anti_join(stop_words, by = "word")
filtered_words
```

then count the words and sort it

```{r}
word_counts <- filtered_words %>%
  count(word, sort = TRUE)
word_counts
```

then plot the top 20 words

```{r}
top_words <- head(word_counts, 20)
ggplot(top_words, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  labs(title = "top 20 Most Common Words in 'Pride and Prejudice'",
       x = "word",
       y = "frequency")+
  coord_flip()
```

## exercise 2

here is my function definition

```{r}
#' Convert to Custom Pig Latin
#'
#' This function converts English words to a custom version of Pig Latin.
#' The rearrangement component involves moving the last letter of the word
#' to the beginning. The addition component adds "xy" to the end of the word.
#'
#' @param word A character string representing a single English word.
#' @return A character string of the word converted to custom Pig Latin.
#' @examples
#' custom_pig_latin("hello")
#' custom_pig_latin("apple")
#' custom_pig_latin("strong")
#' @export
custom_pig_latin <- function(word) {
  # Validate input
  if (!is.character(word) || length(word) != 1) {
    stop("Input must be a single word (character string).")
  }

  if (nchar(word) == 0) {
    return("xy")
  }

  # Check if word starts with a vowel
  if (tolower(substr(word, 1, 1)) %in% c('a', 'e', 'i', 'o', 'u')) {
    # Move the last letter to the start and add "xy"
    return(paste0(substr(word, nchar(word), nchar(word)), substr(word, 1, nchar(word) - 1), "xy"))
  } else {
    # Move the first letter to the end, then the last to the start, and add "xy"
    return(paste0(substr(word, nchar(word), nchar(word)), substr(word, 2, nchar(word) - 1), substr(word, 1, 1), "xy"))
  }
}

```

here is the example

```{r}
custom_pig_latin("hello") # "ohellxy"
custom_pig_latin("apple") # "eapplxy"
custom_pig_latin("strong") # "gstronxy"
```

the test function

```{r}
library(testthat)
```

```{r}
# Begin test cases
test_that("Custom Pig Latin Conversion Works Correctly", {
  expect_equal(custom_pig_latin("hello"), "oellhxy")
  expect_equal(custom_pig_latin("apple"), "eapplxy")
  expect_equal(custom_pig_latin("strong"), "gtronsxy")
})

test_that("Handles Non-Standard Input", {
  expect_error(custom_pig_latin(123))
  expect_error(custom_pig_latin(TRUE))
  expect_error(custom_pig_latin(NULL))
})

test_that("Handles Empty and Single Character Strings", {
  expect_equal(custom_pig_latin(""), "xy")
  expect_equal(custom_pig_latin("a"), "axy")
})
```
